Stat 400 Project

### 2021-11-23 Stat 400 proj.Rmd
Created functions to get step length, step direction, and changes in x,y coordinates.

@@

>>>>

#Random step length function
get_step_length <- function(df, x_dim, y_dim){
  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
  return(step_lengths)
}

#Random step direction function
get_step_direction <- function(length_vec){
  direction <- runif(n=length(length_vec), min=0, max=2*pi)
}

#Get delta_x, delta_y
get_delts <- function(length_vec, direc_vec){
  delta_x <- length_vec * cos(direc_vec)
  delta_y <- length_vec * sin(direc_vec)
  return(cbind(delta_x, delta_y))
}

@@

  for(i in 1:days){
